---
title: "Three Parameters: Causal"
author: "Neelam Arshad"
format: html
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(primer.data)
library(tidymodels)
library(broom)
```

$$
Y_i = \beta_0 + \beta_1 X_{1i} + \beta_2 X_{2i} + \beta_3 X_{3i} + \epsilon_i
$$

$$
\widehat{\text{att\_end}} = 8.45 + 1.55 \times \text{treatment}_{\text{Treated}}
$$

```{r}
#| cache: true
fit_att <- linear_reg(engine = "lm") |> fit(att_end ~ treatment, data = trains)
```

Attitudes toward immigration are an important aspect of public opinion that can be influenced by social and demographic factors and are an increasingly important part of US congressional elections. Using data from a 2012 experiment among Boston commuters, we examine the average causal effect of exposure to Spanish-speakers on people’s attitudes toward immigration among registered voters in Georgia today. Using data from a 2012 survey of Boston-area commuters, we seek to measure the causal effect of exposure to Spanish-speakers on attitudes toward immigration among adults in Chicago and similar cities in 2024. There is some concern that unmeasured factors, such as prior personal experiences with immigrants, could bias the estimated relationship.


